Qeury-Driven Streaming Slot-Value Extraction for Wikipedia Entities at Web-Scale

### 2013-11-04 paper/flairs27/content/discussion.tex
Merged Implementation and system

\section{Discussions \& Conclusion}

@@

>>>>

\section{Discussions}

@@

We sampled documents from the training data period to generate an initial set of patterns. We then use these patterns to generate SSF results. By manully looking at these results, we prune some patterns with poor­performance and add more patterns that we identified from these results. We use several iterations to find the best patterns. We found that it is time consuming to identity quality pattern.

We found three major classes of accuracy errors: incorrect entities selected, incorrect tags by Lingpipe and incorrect pattern extractions. The first issue is ameliorated by generating better aliases . And we use post-processing to reduce the second and third types of errors. We didn't use more advanced NLP packages such as Stanford NLP because of the large size of the data set. The post-processing step to improve the results is discussed in the next section.

\textit{Post Processing Algorithm.}
The SSF output of many extractions is noisy. The data contains duplicates and incorrect extractions. We can define rules to sanitize the output only using the information present in the SSF file. The file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy. We define two classes of rules deduplication rules and inference rules. In our diagram we refer to this component as \textbf{High Accuracy Filter}.
